---
title: "visualization"
output: html_document
date: "2026-10-01"
---

```{r}
library(tidyverse)
library(ggridges)

library(p8105.datasets)
data("weather_df")
```

Now we have everything we need!

```{r}
weather_df
```

Let's make a scatterplot!

```{r}
ggplot(weather_df, aes(x=tmin, y=tmax))+
  geom_point()
```
I always like the daraframe first
```{r}
ggp_temp_scatterplot<-
weather_df |>
  ggplot(aes(x=tmin, y=tmax)) +
  geom_point()

ggp_temp_scatterplot
```
Let's make this a bit fancier...
```{r}
weather_df |>
  ggplot(aes(x=tmin, y=tmax,color=name))+
  geom_point(alpha = .25)+
  geom_smooth(se = FALSE)
```
The aesthetic are up to you.
not necessarily a scatterplot
Show faceting

```{r}
weather_df |>
  ggplot(aes(x=tmin,y=tmax,color=name))+
  geom_point(alpha=.5)+
  facet_grid(. ~ name)
```

```{r}
weather_df |>
  ggplot(aes(x=tmin,y=tmax,color=name))+
  geom_point(alpha=.5)+
  facet_grid(cols=vars(name))
```
Let's look at something else.

```{r}
weather_df |>
  ggplot(aes(x = date,y = tmax,color = name))+
  geom_point(alpha = .5)+
  facet_grid(. ~ name)
```
make a plot of central park tmax v tmin only, and convert temperatures to fahrenheit.

```{r}
weather_df |>
  filter(name=="CentralPark_NY") |>
  mutate(
    tmax = tmax *(9/5) + 32,
    tmin = tmin * (9/5) + 32
  )|>
  ggplot(aes(x=tmin, y=tmax))+
  geom_point()
```

What's a hex plot
```{r}
weather_df |>
  ggplot(aes(x=tmin,y=tmax))+
  geom_hex()
```
# Univeriate glots 单变量
```{r}
weather_df |>
  ggplot(aes(x=tmax))+
  geom_histogram()
```

```{r}
weather_df |>
  ggplot(aes(x=tmax, fill = name))+
  geom_histogram()+
  facet_grid(.~ name)
##分组让其阅读更简单
```
Density plots are great!
```{r}
weather_df |>
  ggplot(aes(x=tmax, fill = name))+ ##color改变曲线颜色，fill填充曲线和x轴
  geom_density(alpha = .3) ##改变透明度
```
Boxplots!

```{r}
weather_df |>
  ggplot(aes(x=name,y=tmax))+ ##x = name, define the boxplot according to name separately
  geom_boxplot()
```
Exist for a long time and popular in 2018^-^
Violin plots

```{r}
weather_df |>
  ggplot(aes(x=name, y=tmax))+
  geom_violin()
```

```{r}
weather_df |> 
  ggplot(aes(x = name, y = tmax)) + 
  geom_violin(aes(fill = name), alpha = .5) + 
  stat_summary(fun = "median", color = "blue")
```

combine density and boxplot = violin

Ridge plots ...

```{r}
weather_df |>
  ggplot(aes(x = tmax, y = name)) +
  geom_density_ridges()
```
if you have 20 categories, difficult to take a look.
ridge plot solves that problem.

## Save some of my plots

```{r}
ggp_weather=
weather_df |>
  ggplot(aes(x=date, y = tmax, color = name))+
  geom_point(aes(size = prcp),alpha = .5)+
  facet_grid(.~ name)

ggp_weather

ggsave("ggp_weather.pdf", ggp_weather) ##save as, save what
```

```{r fig.width =12, fig.height = 12}
weather_df |>
  ggplot(aes(x=tmin,y=tmax)) +
  geom_point()
```